% backmatter/05_tai_lieu_tham_khao.tex
\addcontentsline{toc}{section}{TAI LIEU THAM KHAO}
\begin{thebibliography}{99}

\bibitem{mininet}
Lantz, B., Heller, B., \& McKeown, N. (2010).
\textit{A Network in a Laptop: Rapid Prototyping for Software-Defined Networks}.
Proceedings of the 9th ACM SIGCOMM Workshop on Hot Topics in Networks (Hotnets-IX).

\bibitem{frrouting}
FRRouting Project. (2023).
\textit{FRRouting User Guide}.
Retrieved from \url{https://docs.frrouting.org/en/latest/}

\bibitem{ospf_rfc}
Moy, J. (1998).
\textit{OSPF Version 2} (RFC 2328).
Internet Engineering Task Force (IETF).
Retrieved from \url{https://www.rfc-editor.org/rfc/rfc2328}

\bibitem{nat_rfc}
Srisuresh, P., \& Holdrege, M. (1999).
\textit{IP Network Address Translator (NAT) Terminology and Considerations} (RFC 2663).
Internet Engineering Task Force (IETF).
Retrieved from \url{https://www.rfc-editor.org/rfc/rfc2663}

\bibitem{iptables}
Netfilter Project. (2023).
\textit{iptables -- Administration tool for IPv4/IPv6 packet filtering and NAT}.
Retrieved from \url{https://www.netfilter.org/projects/iptables/}

\bibitem{cisco3tier}
Cisco Systems. (2022).
\textit{Campus Network Design Fundamentals -- Three-Tier Hierarchical Model}.
Retrieved from \url{https://www.cisco.com/c/en/us/td/docs/solutions/Enterprise/Campus/campover.html}

\bibitem{dmz_design}
NIST. (2020).
\textit{Guidelines on Firewalls and Firewall Policy} (Special Publication 800-41 Rev 1).
National Institute of Standards and Technology.
Retrieved from \url{https://csrc.nist.gov/publications/detail/sp/800-41/rev-1/final}

\bibitem{load_balancing}
Bourke, T. (2001).
\textit{Server Load Balancing}.
O'Reilly Media.

\bibitem{python_mininet}
Mininet Team. (2023).
\textit{Mininet Python API Reference}.
Retrieved from \url{http://mininet.org/api/}

\bibitem{matplotlib}
Hunter, J. D. (2007).
\textit{Matplotlib: A 2D Graphics Environment}.
Computing in Science \& Engineering, 9(3), 90--95.

\end{thebibliography}